---
title: "Shiny APP and Presentation Week 4 - Developing Data Products"
author: "Rejane Rodrigues de Carvalho Pereira"
date: "November 26, 2021"
output:
  slidy_presentation: default
---


```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set()
```

## Shiny APP of th Endangered Fauna from Brazil
- The data are based on the Official List 2020 of the Environment Ministery of the Brazilian Government.
- The Brazilian government concerns species threatened with extinction, overexploitation, unsustainable, and - with negative consequences that, sooner or later, will be harmful from the point of view economic, social or environmental.
- This problem requires specific recovery policies for both terrestrial and aquatic fauna and flora.
- More information can be obtained from: http://dados.mma.gov.br/dataset/especies-ameacadas


## Shiny APP of th Endangered Fauna from Brazil

- Shiny application shows the interactive graphics about Brazil' Fauna.
- I published my app on the website: https://www.shinyapps.io/admin/#/application/5211110 with URL https://natureza.shinyapps.io/Developing_Data_Products/
- But if you can't access this because I haven't the Shiny' professional profile, I published the files ui.R and server.R on the github' URL: https://github.com/rodricar/Developing-Data-Products
- The next slides I put the initials steps to download and read the file with its structure.

## Downloading and Reading the File (Code)
```{r read, message=FALSE, warning=FALSE}
library(tidyverse)

fileUrl <- "http://dados.mma.gov.br/dataset/41a79b71-445f-4a6a-8c70-d46af991292a/resource/1f13b062-f3f6-4198-a4c5-3581548bebec/download/lista-de-especies-ameacas-2020.csv"

setwd("C:/Users/Rejane/Documents/Cursos_R/Developing_Data_Products/")

download.file(fileUrl, 
              destfile = "lista-de-especies-ameacas-2020.csv", 
              method = "auto")

endangered_species <- data.table::fread("lista-de-especies-ameacas-2020.csv",                                           encoding = "UTF-8") %>%
janitor::clean_names()
```

## Reading and Structure File

```{r structure, message=FALSE, warning=FALSE}

dplyr::glimpse(endangered_species)

```

## Selecting Data and Plotting Graphics

- Plotting the Fauna' Data as the user-chosen filter Group
- Plotting the the Fauna' Data  as the user-chosen filter Exclusive or Not of Brazil
